
\denseouterlist{
\newline
September 3, 2020

\vspace{5mm} 
\newline


\newline

\newline

\newline


\vspace{5mm}
\newline

Re: lol

\vspace{5mm}
\newline

Dear  ,
\vspace{5mm}
\newline
As the world of technology is expanding quickly,  has became a leading company that develops business software solution to help enterprises manage business operations and customers relations. Being a computer science student with a strong interest in new technologies, I am deeply impressed and admired by how  has developed the most advanced technologies such as  HANA and the cross platform analytic software Lumira, and I am so glad to have the opportunity to obtain a co-op position in  as a software engineer.

\vspace{5mm} 
\newline
I am currently a fourth year computer science student studying at Simon Fraser University. I have gained strong interest in computer science since I am in high school. I have coded class projects and personal projects using Java, C/C++, Python, which gave a solid understanding of computer languages and algorithm. In addition, I have developed a strong understanding of OOP concepts through coding. Most recently, I have worked within a team of three to develop an online turtoring commerce platform. This requires strong technical skills such as coding skills, ability to design UI and database schemas as well as testing abilities. I got myself even more familiar with languages such as HTML, CSS, JavaScript. I was also able to develop soft skills such as teamwork, communication skills and working under pressure to meet aggressive deadlines.

\vspace{5mm} 
\newline

Apart from my studies in field of computer science, I have also pursued a bachelor degree major in statistics. I have actively participated in business statistics related hackthon and competition. I have developed strong cooperative, leadership communication skills while working with students from different backgrounds with different knowledge. So far, I have won two times first place in SFU statistics hackthon, which stood out from over a hundred competitors.

\vspace{5mm} 
\newline

By being involved in multiple technical projects and various competition, I believe that I am a suitable candidate for this position. It would be a valuable and awesome opportunity for me to have a chance to apply the knowledge I gained to real-world industries. I am looking forward to further discuss my qualifications for this role. Please do not hestitate to contact me via SFU co-op office. Thank you for your time!

\vspace{5mm} 
\newline
Sincerely,

\vspace{5mm} 


\vspace{5mm} 
\newline

Jiaran Yu


}
